Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-10-11 src/tf-cutcell-comparison/fig-gravityWaves-theta.tex
add more gravityWaves plots (just for comparison)

\setlength{\parindent}{0pt}
\begin{document}
\centering
\includegraphics[width=6in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffOverview.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-300dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-250dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-250dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-200dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-200dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-150dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-150dz/18000/thetaDiffMountain.pdf}
\end{document}

>>>>

\setlength{\parindent}{0pt}
\begin{document}
\centering
\includegraphics[width=6in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffOverview.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-300dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-250dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-250dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-200dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-200dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-150dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-150dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-100dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-100dz/18000/thetaDiffMountain.pdf}
\vspace*{0.1in}
\includegraphics[width=3in]{../gravityWaves-btf-250m-75dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-75dz/18000/thetaDiffMountain.pdf}
\end{document}
